\documentclass[a4paper,10pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{import}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{pdflscape}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{calc}
\usepackage{float}
\usepackage{amssymb}
\usepackage{listings}
\usepackage[section]{placeins} % don't move figures beyond the next section heading

% this is needed for forms and links within the text
\usepackage{hyperref}

% Variables
\newcommand{\authorName}{
   Mohammed~Abu~Jayyab,
   Niklas~Baumstark,
   Tobias~Gräf,
   Amrei~Loose,
   Christoph~Michel
}
\newcommand{\authorNameEmph}{
   Mohammed~Abu~Jayyab,
   \textbf{Niklas~Baumstark},
   Tobias~Gräf,
   Amrei~Loose,
   Christoph~Michel
}

\newcommand{\dateFirstVersion}{\today}
\newcommand{\customer}{Karlsruhe Institute of Technology}
\newcommand{\contractor}{A company}
\newcommand{\projectName}{Broadcast Encryption\xspace}

\newcommand{\doctitle}{\projectName (Implementation document)}
\title{\doctitle}
\author{\authorName}
\date{\today}

\include{style}

\begin{document}

\input{frontpage}
\tableofcontents
\clearpage

\section{Introduction}
This document contains the changes applied on the implementation with respect to the design document.
Some of these changes were necessary, and then there are additional changes to improve the performance.
The elements as attributes, methods and classes were renamed, whenever it is useful. In the following the 
changes are listed and described according to packages.

\section{Changes in the packages}
\subsection{Package cryptocast.comm}

\begin{itemize}
   \item \textbf{\textit{class DecoratingMessageOutChannel}}
	\begin{itemize}
	 \item This class \textit{"DecoratingMessageOutChannel"} was added for decorating 
	 a message to send with a certain prefix and suffix.
	 \item \textit{"+DecoratingMessageOutChannel(inner: MessageOutChannel, prefix: byte[] , suffix: byte[])"} was added. 
	\end{itemize}
	 
	\item \textbf{\textit{class SimpleHttpStreamServer}}
	\begin{itemize}
	 \item This class \textit{"SimpleHttpStreamServer"} was added for representing a simple tcp based http server.
	 \item \textit{"+SimpleHttpStreamServer(in: InputStream, addr: SocketAddress , contentType:  String , bufsize:  int)"} 
	 was added.
	 \item \textit{"+waitForListener() : int"} was added.
	\end{itemize}
	
   \item \textbf{\textit{class MessageBuffer}}
	\begin{itemize}
	 \item This class \textit{"MessageBuffer"} was added for representing a buffer for all message.
	 \item \textit{"+setBlocking(block: boolean) : void"} was added. 
	 \item \textit{"+close() : void"} was added. 
	\end{itemize}
	
	 \item \textbf{\textit{class StreamUtils}}
	\begin{itemize}
	 \item This class \textit{"StreamUtils"} was added for limiting the number of written bytes per second.
	 \item \textit{"+readall(in: InputStream, buffer: byte[] , offset: int , len: int ) : int"} was added.
	 \item \textit{"+copyInterruptable(in: InputStream , out: OutputStream , bufsize: int) : void"} was added.
	\end{itemize}
	
	 \item \textbf{\textit{class ThrottledOutputStream}}
	\begin{itemize}
	 \item This class \textit{"ThrottledOutputStream"} was added for limiting the number of written bytes per second.
	 \item \textit{"+ThrottledOutputStream(out: OutputStream , maxBytesPerSec: long)"} was added. 
	\end{itemize}
	
   \item \textbf{\textit{class MultiOutputStream}}
  \begin{itemize}
	 \item The class \textit{"MultiOutChannel"} was replaced by this class \textit{"MultiOutputStream"}.
	 \item \textit{"+addChannel(channel : OutChannel) : void"} was replaced by 
	 \textit{"+addChannel(channel : OutputStream ) : void"}.
	 \item \textit{"+removeChannel(channel : OutChannel) : void"} was replaced by 
	 \textit{"+removeChannel(channel : OutputStream ) : void"}.
	 \item \textit{"+send(data : byte[]) : void"} was deleted.
	 \item The static interface \textit{"ErrorHandler"} was added.
	 \item \textit{"+getChannels() : ImmutableList<OutputStream>"} was added.
	 \item \textit{"+MultiOutputStream()"} was added.
	 \item \textit{"+MultiOutputStream(errHandler: ErrorHandler)"} was added.
	 \item \textit{"+handle(multi: MultiOutputStream, channel: OutputStream, exc: IOException) : void"} was added.
	 \item \textit{"+removeOnError : ErrorHandler"} was added.
	 \item \textit{"`+propagateError : ErrorHandler"} was added.
	\end{itemize}
	
   \item \textit{\textbf{class ServerMultiMessageOutChannel}}
	\begin{itemize}
	 \item The class \textit{"SocketMulticastServer"} was replaced by this class \textit{"ServerMultiMessageOutChannel"}.
	 \item \textit{"+SocketMulticastServer(socket : ServerSocket)"} was replaced by 
	 \textit{"+ServerMultiMessageOutChannel(server : ServerSocket , excHandler : Callback<Throwable>)"}.
	 \item \textit{"+send(data : byte[]) : void"} was deleted.
	\end{itemize}
	 
   \item \textbf{\textit{class StatisticalInputStream}}
	\begin{itemize}
	\item The class \textit{"StatisticalInChannel"} was replaced by this class \textit{"StatisticalInputStream"}.
	\item \textit{"+StatisticalInChannel(inner : InChannel)"} was replaced by 
	\textit{"+StatisticalInputStream(inner : InputStream)"}.
	\item \textit{"+recv(size : int, buffer : byte[]) : void"} was deleted.
	\end{itemize}
	
   \item \textbf{\textit{class StatisticalOutputStream}}
	\begin{itemize}
	 \item The class \textit{"StatisticalOutChannel"} was replaced by this class \textit{"StatisticalOutputStream"}.
	 \item \textit{"+StatisticalOutChannel(inner : OutChannel)"} was replaced by 
	 \textit{"+StatisticalOutputStream(inner : OutputStream)"}.
   \item \textit{"+send(data : byte[]) : void"} was deleted.
	\end{itemize}
 
   \item \textbf{\textit{class StreamMessageInChannel}}
	\begin{itemize}
	 \item The class \textit{"MessageInChannel"} was replaced by this \textit{"StreamMessageInChannel"}.
	\end{itemize}
	
   \item \textbf{\textit{class StreamMessageOutChannel}}
	\begin{itemize}
	 \item The class \textit{"MessageOutChannel""} was replaced by this class \textit{"StreamMessageOutChannel"}.
	 \item \textit{"+MessageOutChannel(inner : OutChannel)"} was replaced by 
	 \textit{"+StreamMessageOutChannel(inner : OutputStream)"}.
	 \item \textit{"+sendMessage(data : byte[]) : void"} was replaced by 
	 \textit{"+sendMessage(data: byte[], offset: int , len: int) : void"}.
	\end{itemize}
	
   \item \textbf{\textit{interface MessageInChannel}}
	\begin{itemize}
	 \item The interface \textit{""InChannel"} was renamed to \textit{"MessageInChannel"}.
	 \item \textit{"+recv(size : int, buffer : byte[]) : void"} was replaced by \textit{"+recvMessage() : byte[]"}.
	\end{itemize}
	
	 \item \textbf{\textit{abstract class MessageOutChannel}}
	\begin{itemize}
	 \item The interface \textit{"OutChannel"} was replaced by this abstract class \textit{"MessageOutChannel"}.
	 \item \textit{"+send(data : byte[]) : void"} was renamed to \textit{+sendMessage(data : byte[]) : void"}.
	 \item \textit{"+sendMessage(data: byte[] , offset: int , len: int) : void"} was added.
	\end{itemize}
	
\end{itemize}

\subsection{Package cryptocast.server}
\subsection{Package cryptocast.server.programs}
\subsection{Package cryptocast.client}
\subsection{Package cryptocast.client.filechooser}
\subsection{Package cryptocast.client.bufferedmediaplayer}
\subsection{Package cryptocast.crypto}
\subsection{Package cryptocast.crypto.naorpinkas}
\subsection{Package cryptocast.util}



\end{document}

