\subsection{Package \lstinline!cryptocast.client!}
The client contains an instance of \lstinline|FileChooser|, which can be used to select any file from the SD card 
 of an Android gadget. Since a private key is necessary to encrypt data received from a server the 
 \lstinline|FileChooser| is used to select a keyfile. All servers and responding keyfiles are placed 
 in an instance of \lstinline|ServerHistory| and therefore can be saved and loaded after closing the client.
 Every error is displayed by using a simple pop up window defined by the class \lstinline|ErrorFragment|.
\input{cryptocast.client.custom.tex}
\subsubsection{Class \lstinline|ClientApplication|}
Maintains the global application state. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{ClientApplication}{

}{
+ onCreate() \\
+ saveState() \\
+ getHostnameInput() : String \\
+ setHostnameInput(hostname : String) \\
+ getPortInput() : String \\
+ setPortInput(port : String) \\
+ getWifiOnlyOption() : boolean \\
+ setWifiOnlyOption(isSet : boolean) \\
+ getServerHistory() : ServerHistory \\
+ getServerHistoryHostnames() : String[] \\
+ getServerArray() : InetSocketAddress[] \\
+ getServerStringArray() : String[] \\
+ setServerHistory(serverHistory : ServerHistory)
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|android.app.Application|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onCreate|\lstinline|()| \\[-0.6em]




\item \lstinline|public void| \lstinline|saveState|\lstinline|()|\\ \\[-0.6em]
Saves the application state.



\item \lstinline|public String| \lstinline|getHostnameInput|\lstinline|()|\\ \\[-0.6em]
Returns the hostname input.

\emph{Returns:} The hostname input.

\item \lstinline|public void| \lstinline|setHostnameInput|\lstinline|(String hostname)|\\ \\[-0.6em]
Sets the hostname input.
\begin{itemize}
\item \lstinline|hostname|: The hostname to set.
\end{itemize}



\item \lstinline|public String| \lstinline|getPortInput|\lstinline|()|\\ \\[-0.6em]
Returns the port input.

\emph{Returns:} The port input.

\item \lstinline|public void| \lstinline|setPortInput|\lstinline|(String port)|\\ \\[-0.6em]
Sets the port input.
\begin{itemize}
\item \lstinline|port|: The port to set.
\end{itemize}



\item \lstinline|public boolean| \lstinline|getWifiOnlyOption|\lstinline|()|\\ \\[-0.6em]
\emph{Returns:} whether the Wifi-Only option is set.



\item \lstinline|public void| \lstinline|setWifiOnlyOption|\lstinline|(boolean isSet)|\\ \\[-0.6em]
Sets the Wifi-Only option to the given status.
\begin{itemize}
\item \lstinline|isSet|: The status to set.
\end{itemize}



\item \lstinline|public ServerHistory| \lstinline|getServerHistory|\lstinline|()|\\ \\[-0.6em]
\emph{Returns:} The server history.



\item \lstinline|public String[]| \lstinline|getServerHistoryHostnames|\lstinline|()|\\ \\[-0.6em]
Returns an array of the server history host names

\emph{Returns:} the string array of host names

\item \lstinline|public InetSocketAddress[]| \lstinline|getServerArray|\lstinline|()| \\[-0.6em]




\item \lstinline|public String[]| \lstinline|getServerStringArray|\lstinline|()| \\[-0.6em]




\item \lstinline|public void| \lstinline|setServerHistory|\lstinline|(ServerHistory serverHistory)|\\ \\[-0.6em]
Sets the server history
\begin{itemize}
\item \lstinline|serverHistory|: The server history to set.
\end{itemize}



\end{itemize}

\subsubsection{Class \lstinline|ClientApplication.State|}
The global application state with the respective default values. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{ClientApplication.State}{

}{

}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|java.io.Serializable|
\end{itemize}



\subsubsection{Class \lstinline|StreamViewerActivity|}
This activity is responsible for decrypting the received data
 and viewing it. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{StreamViewerActivity}{

}{
+ onCompletion(p : RawStreamMediaPlayer) \\
+ onError(p : RawStreamMediaPlayer, what : int, extra : int) : boolean \\
+ onError(p : RawStreamMediaPlayer, e : Exception) : boolean \\
+ togglePlay() \\
+ isPlaying() : boolean \\
+ canPause() : boolean \\
+ canSeekBackward() : boolean \\
+ canSeekForward() : boolean \\
+ getBufferPercentage() : int \\
+ getCurrentPosition() : int \\
+ getDuration() : int \\
+ pause() \\
+ seekTo(pos : int) \\
+ start() \\
+ onTouch(arg0 : View, arg1 : MotionEvent) : boolean \\
+ onPrepared(arg0 : RawStreamMediaPlayer) \\
+ createErrorPopup(message : String) \\
+ setStatusText(text : String) \\
+ onInfo(p : RawStreamMediaPlayer, what : int, extra : int)
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|cryptocast.client.ClientActivity|
\item \lstinline|android.view.View.OnTouchListener|
\item \lstinline|android.widget.MediaController.MediaPlayerControl|
\item \lstinline|cryptocast.client.RawStreamMediaPlayer.OnCompletionListener|
\item \lstinline|cryptocast.client.RawStreamMediaPlayer.OnErrorListener|
\item \lstinline|cryptocast.client.RawStreamMediaPlayer.OnInfoListener|
\item \lstinline|cryptocast.client.RawStreamMediaPlayer.OnPreparedListener|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onCompletion|\lstinline|(RawStreamMediaPlayer p)| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|onError|\lstinline|(RawStreamMediaPlayer p, int what, int extra)| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|onError|\lstinline|(RawStreamMediaPlayer p, Exception e)| \\[-0.6em]




\item \lstinline|public void| \lstinline|togglePlay|\lstinline|()|\\ \\[-0.6em]
Toggle playback play/pause. Will pause if in play mode and continue if
 in pause mode.



\item \lstinline|public boolean| \lstinline|isPlaying|\lstinline|()| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|canPause|\lstinline|()| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|canSeekBackward|\lstinline|()| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|canSeekForward|\lstinline|()| \\[-0.6em]




\item \lstinline|public int| \lstinline|getBufferPercentage|\lstinline|()| \\[-0.6em]




\item \lstinline|public int| \lstinline|getCurrentPosition|\lstinline|()| \\[-0.6em]




\item \lstinline|public int| \lstinline|getDuration|\lstinline|()| \\[-0.6em]




\item \lstinline|public void| \lstinline|pause|\lstinline|()| \\[-0.6em]




\item \lstinline|public void| \lstinline|seekTo|\lstinline|(int pos)| \\[-0.6em]




\item \lstinline|public void| \lstinline|start|\lstinline|()| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|onTouch|\lstinline|(View arg0, MotionEvent arg1)| \\[-0.6em]




\item \lstinline|public void| \lstinline|onPrepared|\lstinline|(RawStreamMediaPlayer arg0)| \\[-0.6em]




\item \lstinline|public void| \lstinline|createErrorPopup|\lstinline|(String message)|\\ \\[-0.6em]
Creates a error dialog and finishes the activity on click.
\begin{itemize}
\item \lstinline|message|: the dialog message
\end{itemize}



\item \lstinline|public void| \lstinline|setStatusText|\lstinline|(String text)|\\ \\[-0.6em]
Updates the status label text. Usable from other threads,
\begin{itemize}
\item \lstinline|text|: the text
\end{itemize}



\item \lstinline|public void| \lstinline|onInfo|\lstinline|(RawStreamMediaPlayer p, int what, int extra)| \\[-0.6em]




\end{itemize}

\subsubsection{Class \lstinline|HelpActivity|}
This activity lets a user get help if he needs. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{HelpActivity}{

}{

}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|cryptocast.client.ClientActivity|
\end{itemize}



\subsubsection{Class \lstinline|StreamConnector|}
This class does StreamViewerActivity's work to ensure that the activity is displayed
 correctly. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{StreamConnector}{

}{
+ run() \\
+ stop()
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|java.lang.Runnable|
\end{itemize}


\textbf{\sffamily Constructors}
\begin{itemize}
\item \lstinline|public| \lstinline|StreamConnector|\lstinline|(Socket socket, InetSocketAddress connectAddr, File keyFile, RawStreamMediaPlayer player, StreamViewerActivity streamViewerActivity)|\\ \\[-0.6em]
Creates a SocketConnector with the given socket.
\begin{itemize}
\item \lstinline|socket|: the socket to connect
\item \lstinline|connectAddr|: address to connect to
\item \lstinline|player|: player which will be prepared after connection
\item \lstinline|streamViewerActivity|: activity which contains the statuslabels
\end{itemize}



\end{itemize}


\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|run|\lstinline|()| \\[-0.6em]




\item \lstinline|public void| \lstinline|stop|\lstinline|()|\\ \\[-0.6em]
Stops the connector.



\end{itemize}

\subsubsection{Class \lstinline|ServerHistory|}
This class is responsible for saving recently selected servers
 and their corresponding key files. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{ServerHistory}{

}{
+ getServers() : Map<InetSocketAddress, File> \\
+ getServerList() : List<InetSocketAddress> \\
+ getKeyFile(addr : InetSocketAddress) : Optional<File> \\
+ addServer(addr : InetSocketAddress, keyFile : File) \\
+ deleteServer(addr : InetSocketAddress) \\
+ invalidateKeyFile(addr : InetSocketAddress)
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|java.io.Serializable|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public Map<InetSocketAddress, File>| \lstinline|getServers|\lstinline|()|\\ \\[-0.6em]
Returns the servers and their corresponding key files.

\emph{Returns:} The servers and their corresponding key files.

\item \lstinline|public List<InetSocketAddress>| \lstinline|getServerList|\lstinline|()|\\ \\[-0.6em]
Returns the list which contains the saved servers.

\emph{Returns:} serverlist

\item \lstinline|public Optional<File>| \lstinline|getKeyFile|\lstinline|(InetSocketAddress addr)|\\ \\[-0.6em]
Gets the key file of the given server.
\begin{itemize}
\item \lstinline|addr|: The socket address of the server.
\end{itemize}

\emph{Returns:} The key file of the corresponding server.

\item \lstinline|public void| \lstinline|addServer|\lstinline|(InetSocketAddress addr, File keyFile)|\\ \\[-0.6em]
Adds a server to the list of servers.
\begin{itemize}
\item \lstinline|addr|: The socket address of the server.
\end{itemize}



\item \lstinline|public void| \lstinline|deleteServer|\lstinline|(InetSocketAddress addr)|\\ \\[-0.6em]
Deletes a server from the server history.
\begin{itemize}
\item \lstinline|addr|: The socket address of the server that's deleted.
\end{itemize}



\item \lstinline|public void| \lstinline|invalidateKeyFile|\lstinline|(InetSocketAddress addr)|\\ \\[-0.6em]
Removes a saved key file of the server.
\begin{itemize}
\item \lstinline|addr|: The socket address of the server.
\end{itemize}



\end{itemize}

\subsubsection{Class \lstinline|MainActivity|}
This class represents the activity to connect to the server.
 Before connecting this activity start an instance of \lstinline|KeyChoiceActivity| to
 let the user choose an encryption key file. When the client receives a
 data stream an instance of a \lstinline|StreamViewerActivity| is started to process the
 stream and show its contents. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{MainActivity}{

}{
+ onConnect(view : View) \\
+ onOldServers(view : View)
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|cryptocast.client.ClientActivity|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onConnect|\lstinline|(View view)|\\ \\[-0.6em]
Validates the input and connects to the specified server,
 possibly after letting the user choose a key file.
\begin{itemize}
\item \lstinline|view|: The view from which this method was called.
\end{itemize}



\item \lstinline|public void| \lstinline|onOldServers|\lstinline|(View view)|\\ \\[-0.6em]
Starts a new Server Fragment, showing the list of all servers and a cancel Button.
\begin{itemize}
\item \lstinline|view|: The view from which this method was called.
\end{itemize}



\end{itemize}

\subsubsection{Class \lstinline|ServerListAdapter|}
An adapter between the ListElements and the view showing them. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{ServerListAdapter}{

}{
+ getView(position : int, convertView : View, parent : ViewGroup) : View
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|android.widget.ArrayAdapter<InetSocketAddress>|
\end{itemize}


\textbf{\sffamily Constructors}
\begin{itemize}
\item \lstinline|public| \lstinline|ServerListAdapter|\lstinline|(Context context, List<InetSocketAddress> elements)|\\ \\[-0.6em]
Constructs a new instance with the given attributes.
\begin{itemize}
\item \lstinline|context|: The context in which this adapter is used.
\end{itemize}



\end{itemize}


\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public View| \lstinline|getView|\lstinline|(int position, View convertView, ViewGroup parent)|\\ \\[-0.6em]
\emph{Returns:} A custom view of a list element at the given position in the list.
\begin{itemize}
\item \lstinline|position|: The position of the element in the list
\item \lstinline|convertView|: View which should be converted
\item \lstinline|parent|: The parent view group
\end{itemize}



\end{itemize}

\subsubsection{Class \lstinline|MessageFragment|}
This class is used to pop up an error message. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{MessageFragment}{

}{
+ getMessage() : String \\
+ onCreateDialog(b : Bundle) : Dialog
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|android.support.v4.app.DialogFragment|
\end{itemize}


\textbf{\sffamily Constructors}
\begin{itemize}
\item \lstinline|public| \lstinline|MessageFragment|\lstinline|(String message, OnClickListener clickHandler)|\\ \\[-0.6em]
Creates a new ErrorFragment which can be used to print the given error message.
\begin{itemize}
\item \lstinline|message|: Error message describing the error which occured before this fragment pops up.
\item \lstinline|clickHandler|: The click handler.
\end{itemize}



\item \lstinline|public| \lstinline|MessageFragment|\lstinline|(String message)|\\ \\[-0.6em]
Creates a new ErrorFragment which can be used to print the given error message.
\begin{itemize}
\item \lstinline|message|: Error message describing the error which occured before this fragment pops up.
\end{itemize}



\end{itemize}


\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public String| \lstinline|getMessage|\lstinline|()|\\ \\[-0.6em]
\emph{Returns:} The error message



\item \lstinline|public Dialog| \lstinline|onCreateDialog|\lstinline|(Bundle b)| \\[-0.6em]




\end{itemize}

\subsubsection{Class \lstinline|ClientActivity|}
Defines a client activity. Other activities extend this base activity, which provides basic
 basic common functionality. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[type=abstract]{ClientActivity}{

}{
+ onCreateOptionsMenu(menu : Menu) : boolean \\
+ onOptionsItemSelected(item : MenuItem) : boolean
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|android.support.v4.app.FragmentActivity|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public boolean| \lstinline|onCreateOptionsMenu|\lstinline|(Menu menu)| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|onOptionsItemSelected|\lstinline|(MenuItem item)|\\ \\[-0.6em]
Handles a click on the main menu.
\begin{itemize}
\item \lstinline|item|: The clicked item.
\end{itemize}



\end{itemize}

\subsubsection{Class \lstinline|AboutActivity|}
This activity contains the abouts. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{AboutActivity}{

}{

}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|cryptocast.client.ClientActivity|
\end{itemize}



\subsubsection{Class \lstinline|ServersFragment|}
This class is used to pop up a list of all saved servers. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{ServersFragment}{

}{
+ onCreateDialog(b : Bundle) : Dialog
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|android.support.v4.app.DialogFragment|
\end{itemize}


\textbf{\sffamily Constructors}
\begin{itemize}
\item \lstinline|public| \lstinline|ServersFragment|\lstinline|(ClientApplication app, String message, OnServerSelected callback)|\\ \\[-0.6em]
Creates a servers popup.
\begin{itemize}
\item \lstinline|app|: global application manager
\item \lstinline|message|: the message to display
\item \lstinline|callback|: on selected callback
\end{itemize}



\end{itemize}


\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public Dialog| \lstinline|onCreateDialog|\lstinline|(Bundle b)| \\[-0.6em]




\end{itemize}

\subsubsection{Class \lstinline|OptionsActivity|}
The option screen. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{OptionsActivity}{

}{
+ onCreateContextMenu(menu : ContextMenu, v : View, menuInfo : ContextMenuInfo) \\
+ onContextItemSelected(item : MenuItem) : boolean
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|cryptocast.client.ClientActivity|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onCreateContextMenu|\lstinline|(ContextMenu menu, View v, ContextMenuInfo menuInfo)| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|onContextItemSelected|\lstinline|(MenuItem item)| \\[-0.6em]




\end{itemize}

\subsubsection{Class \lstinline|KeyChoiceActivity|}
This activity lets a user choose an encryption key file
 which is then sent to the server for authentication. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{KeyChoiceActivity}{

}{
+ onCreate(b : Bundle)
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|cryptocast.client.ClientActivity|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onCreate|\lstinline|(Bundle b)| \\[-0.6em]




\end{itemize}

\subsubsection{Class \lstinline|RawStreamMediaPlayer|}
Media player to play audio from a raw \lstinline|InputStream| \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[]{RawStreamMediaPlayer}{

}{
+ setRawDataSource(in : InputStream, contentType : String) \\
+ setOnCompletionListener(completionListener : OnCompletionListener) \\
+ setOnErrorListener(errorListener : OnErrorListener) \\
+ setOnPreparedListener(preparedListener : OnPreparedListener) \\
+ setOnInfoListener(infoListener : OnInfoListener) \\
+ prepare() \\
+ start() \\
+ stop() \\
+ pause() \\
+ onError(p : MediaPlayer, what : int, extra : int) : boolean \\
+ onCompletion(p : MediaPlayer) \\
+ onBufferingUpdate(mp : MediaPlayer, percent : int) \\
+ onPrepared(arg0 : MediaPlayer) \\
+ onInfo(mp : MediaPlayer, what : int, extra : int) : boolean \\
+ isPlaying() : boolean \\
+ onError(e : Exception) : boolean
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}



\textbf{\sffamily Superclasses and Interfaces}
\begin{itemize}
\item \lstinline|android.media.MediaPlayer.OnBufferingUpdateListener|
\item \lstinline|android.media.MediaPlayer.OnCompletionListener|
\item \lstinline|android.media.MediaPlayer.OnErrorListener|
\item \lstinline|android.media.MediaPlayer.OnInfoListener|
\item \lstinline|android.media.MediaPlayer.OnPreparedListener|
\item \lstinline|cryptocast.comm.SimpleHttpStreamServer.OnErrorListener|
\end{itemize}



\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|setRawDataSource|\lstinline|(InputStream in, String contentType)|\\ \\[-0.6em]
Sets the raw data.
\begin{itemize}
\item \lstinline|in|: The input stream.
\item \lstinline|contentType|: The type of content.
\end{itemize}



\item \lstinline|public void| \lstinline|setOnCompletionListener|\lstinline|(OnCompletionListener completionListener)|\\ \\[-0.6em]
Set the on completion listener object.
\begin{itemize}
\item \lstinline|completionListener|: completion listener object to set
\end{itemize}



\item \lstinline|public void| \lstinline|setOnErrorListener|\lstinline|(OnErrorListener errorListener)|\\ \\[-0.6em]
Set the error listener object.
\begin{itemize}
\item \lstinline|errorListener|: error listener object to set.
\end{itemize}



\item \lstinline|public void| \lstinline|setOnPreparedListener|\lstinline|(OnPreparedListener preparedListener)|\\ \\[-0.6em]
Set the prepared listener object.
\begin{itemize}
\item \lstinline|preparedListener|: prepared listener object to set.
\end{itemize}



\item \lstinline|public void| \lstinline|setOnInfoListener|\lstinline|(OnInfoListener infoListener)|\\ \\[-0.6em]
Set the info listener object.



\item \lstinline|public void| \lstinline|prepare|\lstinline|()|\\ \\[-0.6em]
Prepares the player with a data source and event listeners.



\item \lstinline|public void| \lstinline|start|\lstinline|()|\\ \\[-0.6em]
Starts the media player.



\item \lstinline|public void| \lstinline|stop|\lstinline|()|\\ \\[-0.6em]
Stops the media player.



\item \lstinline|public void| \lstinline|pause|\lstinline|()|\\ \\[-0.6em]
Pauses the media player.



\item \lstinline|public boolean| \lstinline|onError|\lstinline|(MediaPlayer p, int what, int extra)| \\[-0.6em]




\item \lstinline|public void| \lstinline|onCompletion|\lstinline|(MediaPlayer p)| \\[-0.6em]




\item \lstinline|public void| \lstinline|onBufferingUpdate|\lstinline|(MediaPlayer mp, int percent)| \\[-0.6em]




\item \lstinline|public void| \lstinline|onPrepared|\lstinline|(MediaPlayer arg0)| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|onInfo|\lstinline|(MediaPlayer mp, int what, int extra)| \\[-0.6em]




\item \lstinline|public boolean| \lstinline|isPlaying|\lstinline|()|\\ \\[-0.6em]
\emph{Returns:} whether the player is playing



\item \lstinline|public boolean| \lstinline|onError|\lstinline|(Exception e)| \\[-0.6em]




\end{itemize}

\subsubsection{Interface \lstinline|ServersFragment.OnServerSelected|}
On server selected interface. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[type=abstract]{ServersFragment.OnServerSelected}{

}{
\umlvirt{+ onServerSelected(addr : InetSocketAddress)}
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}





\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onServerSelected|\lstinline|(InetSocketAddress addr)|\\ \\[-0.6em]
Called on server selection.
\begin{itemize}
\item \lstinline|addr|: selected address
\end{itemize}



\end{itemize}

\subsubsection{Interface \lstinline|RawStreamMediaPlayer.OnCompletionListener|}
Interface for completion callback. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[type=abstract]{RawStreamMediaPlayer.OnCompletionListener}{

}{
\umlvirt{+ onCompletion(p : RawStreamMediaPlayer)}
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}





\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onCompletion|\lstinline|(RawStreamMediaPlayer p)|\\ \\[-0.6em]
Called after completion.
\begin{itemize}
\item \lstinline|p|: The media player.
\end{itemize}



\end{itemize}

\subsubsection{Interface \lstinline|RawStreamMediaPlayer.OnErrorListener|}
Interface for error callback. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[type=abstract]{RawStreamMediaPlayer.OnErrorListener}{

}{
\umlvirt{+ onError(p : RawStreamMediaPlayer, what : int, extra : int) : boolean} \\
\umlvirt{+ onError(p : RawStreamMediaPlayer, e : Exception) : boolean}
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}





\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public boolean| \lstinline|onError|\lstinline|(RawStreamMediaPlayer p, int what, int extra)|\\ \\[-0.6em]
Called if any error occurs in the media player.
\begin{itemize}
\item \lstinline|p|: The media player.
\item \lstinline|what|: The error code.
\item \lstinline|extra|: Extra info
\end{itemize}

\emph{Returns:} true, if the error was handled, false otherwise

\item \lstinline|public boolean| \lstinline|onError|\lstinline|(RawStreamMediaPlayer p, Exception e)|\\ \\[-0.6em]
Called if any error occurs in the HTTP server.
\begin{itemize}
\item \lstinline|p|: The media player.
\item \lstinline|e|: The exception
\end{itemize}

\emph{Returns:} true, if the error was handled, false otherwise

\end{itemize}

\subsubsection{Interface \lstinline|RawStreamMediaPlayer.OnPreparedListener|}
Interface for on prepared callback. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[type=abstract]{RawStreamMediaPlayer.OnPreparedListener}{

}{
\umlvirt{+ onPrepared(p : RawStreamMediaPlayer)}
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}





\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onPrepared|\lstinline|(RawStreamMediaPlayer p)|\\ \\[-0.6em]
Called if player is prepared.
\begin{itemize}
\item \lstinline|p|: The media player.
\end{itemize}



\end{itemize}

\subsubsection{Interface \lstinline|RawStreamMediaPlayer.OnInfoListener|}
Interface for on info callback. \\
\noindent\begin{minipage}[t]{5cm}
\vspace{0.3em}
\hspace*{2em}
\begin{tikzpicture}
\umlclass[type=abstract]{RawStreamMediaPlayer.OnInfoListener}{

}{
\umlvirt{+ onInfo(p : RawStreamMediaPlayer, what : int, extra : int)}
}
\end{tikzpicture}
\vspace{0.3em}
\end{minipage}





\textbf{\sffamily Methods}
\begin{itemize}
\item \lstinline|public void| \lstinline|onInfo|\lstinline|(RawStreamMediaPlayer p, int what, int extra)|\\ \\[-0.6em]
Called if player provides new info.
\begin{itemize}
\item \lstinline|p|: The media player.
\end{itemize}



\end{itemize}


